\documentclass[a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[scaled=.9]{helvet}
\usepackage{courier}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\widowpenalty=10000
\clubpenalty=10000

\title{\LARGE XMI2TGSchema\\Manual}

\begin{document}

	\maketitle
	\vspace{-6pt}
	
	\section{Purpose}
	The tool \emph{XMI2TGSchema} transforms a TGraph schema specified by a grUML model in XMI-format to a corresponding TGraph schema definition in TG-format, readable by JGraLab. The possible deviations from grUML the tool is able to cope with are given in the descriptions of the \texttt{autoCorrect} parameter in section \ref{sec:Usage}. Up to now, the transformation has only been tested for XMI-files exported by Sparx System's \emph{Enterprise Architect}.
	
	\section{Prerequisites}
	As XMI2TGSchema is implemented as an XSL Stylesheet, an XSLT processor is needed for its execution. The processor must be capable of processing XSLT 2.0. The usage instruction below relate to \emph{Saxon-B}, available at \emph{http://www.saxonica.com}. The tested version of Saxon-B is 9.0.0.2J.
	
	\section{Usage} \label{sec:Usage}
	The command line instruction is:
	
	\texttt{java -jar saxon9.jar } \texttt{-s:}\emph{source}\texttt{ -xsl:}\emph{path}\texttt{/XMI2TGSchema.xsl} \\
	\mbox{[}\texttt{-o:}\emph{target}] \\
	\texttt{schemaName=}\emph{schemaName} \\
	\mbox{[}\texttt{tool=}\emph{tool}]\texttt{ }[\texttt{appendEdgeIds=}(\texttt{yes}|\texttt{no})]\texttt{ }[\texttt{autoCorrect=}(\texttt{yes}|\texttt{no})] \\
	\mbox{[}\texttt{errorDetection=}(\texttt{yes}|\texttt{no})]\texttt{ }[\texttt{extendedEdgeClassNames=}(\texttt{yes}|\texttt{no})] \\
	\mbox{[}\texttt{uml=}(\texttt{yes}|\texttt{no})] \\

	with the following mandatory parameters:
	\begin{itemize}
		\item \emph{source} -- The XMI-file to be transformed.
		\item \emph{path} -- The path to the XSL stylesheet \texttt{XMI2TGSchema.xsl}.
		\item \emph{schemaName} -- Defines the name of the created Schema. The name must correspond to the UML package in the modeling tool which contains the schema (e.\ g.\ \texttt{de.uni-koblenz.jgstreetmap.JgStreetMap}). If the package does not contain a class with stereotype \texttt{<<GraphClass>>}, the name of the created GraphClass is \texttt{DefaultGraphClass}.
	\end{itemize}
	
	The following parameters are optional:
	\begin{itemize}
		\item \emph{target} -- The output file. If not given, the standard output device (usually the screen) is used.
		\item \emph{appendEdgeIds} -- If set to \texttt{yes}, ids of associations are added to the names of corresponding EdgeClasses. This helps to avoid duplicate names, but makes code harder to understand. Default is \texttt{no}.
		\item \emph{autoCorrect} -- If set to \texttt{yes}, the following corrections are made:
		\begin{itemize}
			\item If the first character of Vertex Class and Edge Class names is lower case, it is set to upper case.
			\item Identifiers conflicting with reserved words are modified by prepending an apostrophe (').
			\item If an Edge Class has no name, it is created by using role names or the names of the incident Vertex Classes. 
		\end{itemize}
		It is recommended to set this parameter to \texttt{yes}. Default is \texttt{yes}.
		\item \emph{errorDetection} -- If set to \texttt{yes},
		\begin{itemize}
			\item Vertex Classes without names are detected and an error is thrown.
			\item Vertex Classes with duplicate names are detected and an error is thrown.
			\item a Schema which is not self-contained is detected and an error is thrown\footnote{Most probably an association in the XMI-file is to be transformed to an Edge Class, but one of the associated Classes is not in the schema package.}.
		\end{itemize}
		It is recommended to set this parameter to \texttt{yes}. Default is \texttt{yes}.
		\item \emph{extendedEdgeClassNames} --  If set to \texttt{yes} generated Edge Class names correspond to the extended form \emph{FromRolename}\texttt{LinksTo}\emph{ToRolename}, else names correspond to \texttt{LinksTo}\emph{ToRolename}. Default is \texttt{no}.
		\item \emph{tool} -- The tool used to create the XMI file. As yet, the only possible value is \texttt{ea}. Omission of this parameter probably results in corrupted TG files (e.g.\ due to missing attribute types).
		\item \emph{uml} -- If set to \texttt{yes}, the grUML equivalents of the following UML constructs are created:
		\begin{itemize}
			\item associations with \emph{derived union} association end => \emph{abstract} edge classes
			\item associations with subsetting association end => EdgeClass as specialization of edge class corresponding to association with subsetted association end.
		\end{itemize}
		Default is \texttt{no}.
	\end{itemize}
	
	\section{Notes}
	\subsection{Conversion of Associations in Enterprise Architect}
	As it is not possible to directly specify package containment for associations in Enterprise Architect, the containment in the exported XMI is derived from the classes connected by the association.

	The following observations were made:
	\begin{itemize}
		\item If both classes reside in the same package, the association is also considered to be in this package.
		\item If one class resides in a package which is ``above'' the other class's package in the package hierarchy, the association is considered to be in the package on the higher hierarchy level.
		\item If the classes reside in different packages on the same hierarchy level, package containment for the concerned association seems to be random.
	\end{itemize}
	
	\subsection{Attribute Types in Enterprise Architect}
	The domains of attributes have to be spelled \emph{exactly} as defined by the grUML specification (e.g.\ Integer, Boolean, Double, etc.). The range of predefined primitive attribute types provided by Enterprise Architect depends on the setting of the ``\emph{Language}'' option for a class or association class. The default setting, ``Java'', is not suitable for grUML models because the Java type names differ significantly from the grUML domain names. 

	In order to avoid tedious typing of domain names for every attribute, EA allows for defining a new language (grUML) together with its attribute types by selecting the \emph{Settings $\rightarrow$ Code Datatypes} menu item. This language can then be set as default with the \emph{Code Generation} toolbar. If this toolbar is not visible, select the \emph{View $\rightarrow$ Toolbars $\rightarrow$ Code Generation} menu item.
	
	However, the composite domains \texttt{List} and \texttt{Set} still require manual typing.
	
\end{document}